Computing Exact Restricted Isometry Constants via Mixed Integer Semidefinite Programming

### 2016-03-20 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
paper: minor modifications w.r.t. RIC

Since the following results depend on the constant $\delta$ in \eqref{rip} being
small enough, we are generally interested in the smallest constant satisfying
\eqref{rip}.

@@

\begin{theorem}[Cand\'es~\cite{Can08}]\label{RIPsqrt2}
  Let $A$ satisfy $\delta_{2k} < \sqrt{2}-1 \approx 0.4142$. If there
  exists $\tilde{x} \in \R^n$ with $\Norm{\tilde{x}}{0} \leq k$ and
  $A\tilde{x} = b$, then the optimal solutions of~\eqref{l0min}
  and~\eqref{l1min} coincide.
\end{theorem}

>>>>

Since the following results depend on the constant $\delta$ in \eqref{rip} being
small enough, one is generally interested in the smallest constant satisfying
\eqref{rip}.

@@

\begin{theorem}[Cand\'es~\cite{Can08}]\label{RIPsqrt2}
  Let the RIC of order $2k$ of $A$ satisfy $\delta_{2k} < \sqrt{2}-1 \approx 0.4142$. If there
  exists $\tilde{x} \in \R^n$ with $\Norm{\tilde{x}}{0} \leq k$ and
  $A\tilde{x} = b$, then the optimal solutions of~\eqref{l0min}
  and~\eqref{l1min} coincide.
\end{theorem}
